\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-14 article.tex
Cleanup

\begin{figure}[H]
     \centering
     \begin{minipage}[b]{0.32\textwidth}
\begin{minted}[bgcolor=LightGray]{gas}
# ...
movslq 0xc(%rsp),%rax
cmp    0x10(%rsp),%rax
jae    0x1199 <main+89>
mov    0xc(%rsp),%eax
add    $0x1,%eax
mov    %eax,0xc(%rsp)
jmp    0x1179 <main+57>
# ...
     \end{minted}
     \caption{TODO}\label{fig:clang-loop}
   \end{minipage}
   \begin{minipage}[b]{0.65\textwidth}
   \begin{minipage}[b]{0.50\textwidth}
  \begin{minted}[bgcolor=LightGray]{gas}
# ...
movq	%rsi, %rax
movl	(%rax), %eax
movq	$0, %rdx
movl	%eax, %edx
movq	%rdx, %rax
movq	$0, %rbx
movl	%eax, %ebx
movq	%rdi, %rax
movq	(%rax), %rax
movq	%rax, %rdx
     \end{minted}
   \end{minipage}
   \begin{minipage}[b]{0.50\textwidth}
  \begin{minted}[bgcolor=LightGray]{gas}
movq	%rax, %rdx
movq	%rbx, %rax
movq	%rdx, %rcx
cmpq	%rcx, %rax
movq	$0, %rdx
setb	%dl
movq	%rdx, %rax
cmpq	$0, %rax
je	_main$20
jmp	_main$17
# ...
     \end{minted}
   \end{minipage}
     \caption{TODO}\label{fig:my-loop0}
   \end{minipage}
\end{figure}
\noindent It does make sense that my compiler nearly takes 3x as many cycles considering that nearly 3x as many instructions are being executed.   Because od the way values are stored, there is literally no benefit from Briggs coalescing since no phi nodes are involved ever.
I was surprised to see Greedy and Linear 2 to be that much slower, but on second thought it makes perfect sense since loading variables from the stack before every single arithmetic/logic operation is considerably slower. What's more surprising is the fact that Tiger is nearly 4x faster than any Greedy (see Table \ref{tab:loopn0.tig}).
It's presumably just because all binary operations consist of  about three instructions or so.

@@

Integer factorization is another interesting algorithm. Generally considered to be NP, here are the results of factorizing known primes of inreasing bit length:

@@

\caption{\label{tab:factori64}Benchmark of \texttt{benches/factori64.ll} output by \mintinline{bash}{dune exec bench -- -f factori32 -n 1024}}

@@

@@

@@

arg(s) & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear 2 & linear 12 & greedy 12 & greedy 0 \\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 150790& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99873x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00204x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00055x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00202x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00475x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99925x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99983x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00036x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 266858& \cellcolor[rgb]{0.939453125,0.9990234375,0.75} 1.76227x& \cellcolor[rgb]{0.951171875,0.9990234375,0.75} 1.81025x& \cellcolor[rgb]{0.8095703125,0.9990234375,0.75} 1.24026x& \cellcolor[rgb]{0.93359375,0.9990234375,0.75} 1.73967x& \cellcolor[rgb]{0.93359375,0.9990234375,0.75} 1.73845x& \cellcolor[rgb]{0.9326171875,0.9990234375,0.75} 1.73599x& \cellcolor[rgb]{0.939453125,0.9990234375,0.75} 1.76279x& \cellcolor[rgb]{0.9990234375,0.8681640625,0.75} 6.18927x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 332932& \cellcolor[rgb]{0.8681640625,0.9990234375,0.75} 1.47463x& \cellcolor[rgb]{0.896484375,0.9990234375,0.75} 1.58958x& \cellcolor[rgb]{0.7734375,0.9990234375,0.75} 1.09780x& \cellcolor[rgb]{0.7978515625,0.9990234375,0.75} 1.19567x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39187x& \cellcolor[rgb]{0.84765625,0.9990234375,0.75} 1.39397x& \cellcolor[rgb]{0.86328125,0.9990234375,0.75} 1.45798x& \cellcolor[rgb]{0.9990234375,0.8955078125,0.75} 5.30079x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 396964& \cellcolor[rgb]{0.873046875,0.9990234375,0.75} 1.49802x& \cellcolor[rgb]{0.89453125,0.9990234375,0.75} 1.58318x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03435x& \cellcolor[rgb]{0.7607421875,0.9990234375,0.75} 1.04439x& \cellcolor[rgb]{0.8310546875,0.9990234375,0.75} 1.32655x& \cellcolor[rgb]{0.7919921875,0.9990234375,0.75} 1.16965x& \cellcolor[rgb]{0.8330078125,0.9990234375,0.75} 1.33411x& \cellcolor[rgb]{0.9990234375,0.916015625,0.75} 4.64216x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 463143& \cellcolor[rgb]{0.8193359375,0.9990234375,0.75} 1.27994x& \cellcolor[rgb]{0.8916015625,0.9990234375,0.75} 1.56894x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00193x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00219x& \cellcolor[rgb]{0.802734375,0.9990234375,0.75} 1.21525x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00036x& \cellcolor[rgb]{0.9990234375,0.9375,0.75} 3.97536x& \cellcolor[rgb]{0.9990234375,0.9208984375,0.75} 4.50366x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 528926& \cellcolor[rgb]{0.841796875,0.9990234375,0.75} 1.37202x& \cellcolor[rgb]{0.904296875,0.9990234375,0.75} 1.62053x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00265x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00090x& \cellcolor[rgb]{0.7958984375,0.9990234375,0.75} 1.18442x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00260x& \cellcolor[rgb]{0.9990234375,0.94921875,0.75} 3.59263x& \cellcolor[rgb]{0.9990234375,0.921875,0.75} 4.46336x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 594806& \cellcolor[rgb]{0.818359375,0.9990234375,0.75} 1.27651x& \cellcolor[rgb]{0.9013671875,0.9990234375,0.75} 1.60931x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.91222x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.92581x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16478x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.89116x& \cellcolor[rgb]{0.9990234375,0.955078125,0.75} 3.38589x& \cellcolor[rgb]{0.9990234375,0.921875,0.75} 4.46530x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 660398& \cellcolor[rgb]{0.84765625,0.9990234375,0.75} 1.39599x& \cellcolor[rgb]{0.9013671875,0.9990234375,0.75} 1.60987x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.89423x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90015x& \cellcolor[rgb]{0.7861328125,0.9990234375,0.75} 1.14754x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90032x& \cellcolor[rgb]{0.9990234375,0.96484375,0.75} 3.08470x& \cellcolor[rgb]{0.9990234375,0.935546875,0.75} 4.02611x\\
\caption{\label{tab:dumb-fib-greedy}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}

\subsubsection{\lstinline!benches/factori64.ll!}
268435399 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 218996& \cellcolor[rgb]{0.7666015625,0.9990234375,0.75} 1.07020x& \cellcolor[rgb]{0.7763671875,0.9990234375,0.75} 1.10754x& \cellcolor[rgb]{0.767578125,0.9990234375,0.75} 1.07114x& \cellcolor[rgb]{0.7763671875,0.9990234375,0.75} 1.10950x& \cellcolor[rgb]{0.7744140625,0.9990234375,0.75} 1.09908x& \cellcolor[rgb]{0.90234375,0.9990234375,0.75} 1.61452x& \cellcolor[rgb]{0.9990234375,0.986328125,0.75} 2.38305x& \cellcolor[rgb]{0.9990234375,0.986328125,0.75} 2.38509x\\
536870909 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 247101& \cellcolor[rgb]{0.7705078125,0.9990234375,0.75} 1.08257x& \cellcolor[rgb]{0.7822265625,0.9990234375,0.75} 1.13159x& \cellcolor[rgb]{0.7705078125,0.9990234375,0.75} 1.08546x& \cellcolor[rgb]{0.7822265625,0.9990234375,0.75} 1.13164x& \cellcolor[rgb]{0.783203125,0.9990234375,0.75} 1.13364x& \cellcolor[rgb]{0.947265625,0.9990234375,0.75} 1.79438x& \cellcolor[rgb]{0.9990234375,0.9755859375,0.75} 2.73111x& \cellcolor[rgb]{0.9990234375,0.9755859375,0.75} 2.73643x\\
1073741789 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 285989& \cellcolor[rgb]{0.775390625,0.9990234375,0.75} 1.10503x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16197x& \cellcolor[rgb]{0.775390625,0.9990234375,0.75} 1.10359x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16233x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16392x& \cellcolor[rgb]{0.9912109375,0.9990234375,0.75} 1.97079x& \cellcolor[rgb]{0.9990234375,0.9638671875,0.75} 3.11293x& \cellcolor[rgb]{0.9990234375,0.9638671875,0.75} 3.12110x\\
2147483647 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 341802& \cellcolor[rgb]{0.779296875,0.9990234375,0.75} 1.12053x& \cellcolor[rgb]{0.7958984375,0.9990234375,0.75} 1.18807x& \cellcolor[rgb]{0.7802734375,0.9990234375,0.75} 1.12297x& \cellcolor[rgb]{0.7978515625,0.9990234375,0.75} 1.19256x& \cellcolor[rgb]{0.796875,0.9990234375,0.75} 1.19163x& \cellcolor[rgb]{0.9990234375,0.994140625,0.75} 2.14407x& \cellcolor[rgb]{0.9990234375,0.9521484375,0.75} 3.49973x& \cellcolor[rgb]{0.9990234375,0.951171875,0.75} 3.50847x\\
4294967291 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 419941& \cellcolor[rgb]{0.78515625,0.9990234375,0.75} 1.14339x& \cellcolor[rgb]{0.8046875,0.9990234375,0.75} 1.22187x& \cellcolor[rgb]{0.78515625,0.9990234375,0.75} 1.14366x& \cellcolor[rgb]{0.8046875,0.9990234375,0.75} 1.22078x& \cellcolor[rgb]{0.8046875,0.9990234375,0.75} 1.22093x& \cellcolor[rgb]{0.9990234375,0.98828125,0.75} 2.31858x& \cellcolor[rgb]{0.9990234375,0.9404296875,0.75} 3.87528x& \cellcolor[rgb]{0.9990234375,0.939453125,0.75} 3.88825x\\
8589934583 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 530002& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16154x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24776x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16318x& \cellcolor[rgb]{0.810546875,0.9990234375,0.75} 1.24673x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24866x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.47972x& \cellcolor[rgb]{0.9990234375,0.9296875,0.75} 4.22355x& \cellcolor[rgb]{0.9990234375,0.9287109375,0.75} 4.23487x\\
17179869143 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 685889& \cellcolor[rgb]{0.7939453125,0.9990234375,0.75} 1.17835x& \cellcolor[rgb]{0.8173828125,0.9990234375,0.75} 1.27310x& \cellcolor[rgb]{0.7939453125,0.9990234375,0.75} 1.17878x& \cellcolor[rgb]{0.8173828125,0.9990234375,0.75} 1.27365x& \cellcolor[rgb]{0.8173828125,0.9990234375,0.75} 1.27361x& \cellcolor[rgb]{0.9990234375,0.9794921875,0.75} 2.61753x& \cellcolor[rgb]{0.9990234375,0.919921875,0.75} 4.52244x& \cellcolor[rgb]{0.9990234375,0.919921875,0.75} 4.53682x\\
34359738337 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 905070& \cellcolor[rgb]{0.796875,0.9990234375,0.75} 1.19204x& \cellcolor[rgb]{0.8232421875,0.9990234375,0.75} 1.29498x& \cellcolor[rgb]{0.7978515625,0.9990234375,0.75} 1.19218x& \cellcolor[rgb]{0.8232421875,0.9990234375,0.75} 1.29535x& \cellcolor[rgb]{0.8232421875,0.9990234375,0.75} 1.29450x& \cellcolor[rgb]{0.9990234375,0.9755859375,0.75} 2.73632x& \cellcolor[rgb]{0.9990234375,0.912109375,0.75} 4.77726x& \cellcolor[rgb]{0.9990234375,0.912109375,0.75} 4.79190x\\
\caption{\label{tab:factori64-table}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}
128 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 159130& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00777x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00293x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00644x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01562x& \cellcolor[rgb]{0.8173828125,0.9990234375,0.75} 1.27104x& \cellcolor[rgb]{0.82421875,0.9990234375,0.75} 1.29856x& \cellcolor[rgb]{0.82421875,0.9990234375,0.75} 1.29894x\\
256 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 163800& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00726x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01200x& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.00852x& \cellcolor[rgb]{0.7529296875,0.9990234375,0.75} 1.01440x& \cellcolor[rgb]{0.8818359375,0.9990234375,0.75} 1.53225x& \cellcolor[rgb]{0.89453125,0.9990234375,0.75} 1.58048x& \cellcolor[rgb]{0.8974609375,0.9990234375,0.75} 1.59431x\\
512 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 172096& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01902x& \cellcolor[rgb]{0.755859375,0.9990234375,0.75} 1.02488x& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01789x& \cellcolor[rgb]{0.75390625,0.9990234375,0.75} 1.01876x& \cellcolor[rgb]{0.9990234375,0.9970703125,0.75} 2.03762x& \cellcolor[rgb]{0.9990234375,0.994140625,0.75} 2.13731x& \cellcolor[rgb]{0.9990234375,0.9931640625,0.75} 2.15792x\\
1024 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 188591& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03687x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03706x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.02964x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03689x& \cellcolor[rgb]{0.9990234375,0.9697265625,0.75} 2.93413x& \cellcolor[rgb]{0.9990234375,0.9638671875,0.75} 3.09867x& \cellcolor[rgb]{0.9990234375,0.962890625,0.75} 3.15326x\\
2048 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 221875& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04971x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06586x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04806x& \cellcolor[rgb]{0.765625,0.9990234375,0.75} 1.06306x& \cellcolor[rgb]{0.9990234375,0.92578125,0.75} 4.34620x& \cellcolor[rgb]{0.9990234375,0.916015625,0.75} 4.64145x& \cellcolor[rgb]{0.9990234375,0.9140625,0.75} 4.72466x\\
4096 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 288132& \cellcolor[rgb]{0.771484375,0.9990234375,0.75} 1.08649x& \cellcolor[rgb]{0.7744140625,0.9990234375,0.75} 1.09864x& \cellcolor[rgb]{0.76953125,0.9990234375,0.75} 1.08082x& \cellcolor[rgb]{0.7744140625,0.9990234375,0.75} 1.10033x& \cellcolor[rgb]{0.9990234375,0.8662109375,0.75} 6.25886x& \cellcolor[rgb]{0.9990234375,0.8525390625,0.75} 6.69614x& \cellcolor[rgb]{0.9990234375,0.84765625,0.75} 6.84597x\\
8192 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 424179& \cellcolor[rgb]{0.7763671875,0.9990234375,0.75} 1.10601x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12721x& \cellcolor[rgb]{0.7763671875,0.9990234375,0.75} 1.10683x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12700x& \cellcolor[rgb]{0.9990234375,0.8037109375,0.75} 8.26470x& \cellcolor[rgb]{0.9990234375,0.78515625,0.75} 8.85856x& \cellcolor[rgb]{0.9990234375,0.7783203125,0.75} 9.07318x\\
16384 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 697378& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12603x& \cellcolor[rgb]{0.787109375,0.9990234375,0.75} 1.15191x& \cellcolor[rgb]{0.78125,0.9990234375,0.75} 1.12581x& \cellcolor[rgb]{0.787109375,0.9990234375,0.75} 1.15269x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.00521x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.73828x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 10.98249x\\

@@

\begin{table}[H]
\makebox[\textwidth][c]{
\begin{NiceTabular}{|c|ccccccccc|}
\hline
arg(s) & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear 12 & linear 2 & greedy 12 & greedy 0 \\
\hline
4 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 171300& \cellcolor[rgb]{0.751953125,0.9990234375,0.75} 1.01148x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.02792x& \cellcolor[rgb]{0.755859375,0.9990234375,0.75} 1.02449x& \cellcolor[rgb]{0.755859375,0.9990234375,0.75} 1.02731x& \cellcolor[rgb]{0.7880859375,0.9990234375,0.75} 1.15660x& \cellcolor[rgb]{0.7841796875,0.9990234375,0.75} 1.13751x& \cellcolor[rgb]{0.8173828125,0.9990234375,0.75} 1.27163x& \cellcolor[rgb]{0.8037109375,0.9990234375,0.75} 1.21946x\\
5 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 189030& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04909x& \cellcolor[rgb]{0.771484375,0.9990234375,0.75} 1.08923x& \cellcolor[rgb]{0.7626953125,0.9990234375,0.75} 1.05266x& \cellcolor[rgb]{0.7705078125,0.9990234375,0.75} 1.08530x& \cellcolor[rgb]{0.8486328125,0.9990234375,0.75} 1.39953x& \cellcolor[rgb]{0.85546875,0.9990234375,0.75} 1.42370x& \cellcolor[rgb]{0.9033203125,0.9990234375,0.75} 1.61577x& \cellcolor[rgb]{0.908203125,0.9990234375,0.75} 1.63543x\\
6 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 305772& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24795x& \cellcolor[rgb]{0.830078125,0.9990234375,0.75} 1.32393x& \cellcolor[rgb]{0.8125,0.9990234375,0.75} 1.25272x& \cellcolor[rgb]{0.83203125,0.9990234375,0.75} 1.33146x& \cellcolor[rgb]{0.9990234375,0.9873046875,0.75} 2.34850x& \cellcolor[rgb]{0.9990234375,0.9873046875,0.75} 2.37422x& \cellcolor[rgb]{0.9990234375,0.9609375,0.75} 3.21562x& \cellcolor[rgb]{0.9990234375,0.9599609375,0.75} 3.23381x\\
7 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1331652& \cellcolor[rgb]{0.86328125,0.9990234375,0.75} 1.45633x& \cellcolor[rgb]{0.90625,0.9990234375,0.75} 1.62799x& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.50098x& \cellcolor[rgb]{0.9091796875,0.9990234375,0.75} 1.64250x& \cellcolor[rgb]{0.9990234375,0.9580078125,0.75} 3.31242x& \cellcolor[rgb]{0.9990234375,0.955078125,0.75} 3.39020x& \cellcolor[rgb]{0.9990234375,0.904296875,0.75} 5.03373x& \cellcolor[rgb]{0.9990234375,0.9033203125,0.75} 5.06248x\\
8 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 11197605& \cellcolor[rgb]{0.904296875,0.9990234375,0.75} 1.62006x& \cellcolor[rgb]{0.9375,0.9990234375,0.75} 1.75454x& \cellcolor[rgb]{0.89453125,0.9990234375,0.75} 1.58268x& \cellcolor[rgb]{0.939453125,0.9990234375,0.75} 1.76405x& \cellcolor[rgb]{0.9990234375,0.9482421875,0.75} 3.61197x& \cellcolor[rgb]{0.9990234375,0.9482421875,0.75} 3.62996x& \cellcolor[rgb]{0.9990234375,0.8876953125,0.75} 5.56708x& \cellcolor[rgb]{0.9990234375,0.888671875,0.75} 5.53880x\\
9 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 112923594& \cellcolor[rgb]{0.9140625,0.9990234375,0.75} 1.66209x& \cellcolor[rgb]{0.9541015625,0.9990234375,0.75} 1.82157x& \cellcolor[rgb]{0.904296875,0.9990234375,0.75} 1.62219x& \cellcolor[rgb]{0.9453125,0.9990234375,0.75} 1.78657x& \cellcolor[rgb]{0.9990234375,0.947265625,0.75} 3.65915x& \cellcolor[rgb]{0.9990234375,0.94140625,0.75} 3.82090x& \cellcolor[rgb]{0.9990234375,0.880859375,0.75} 5.79421x& \cellcolor[rgb]{0.9990234375,0.8818359375,0.75} 5.75327x\\
10 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1348654063& \cellcolor[rgb]{0.884765625,0.9990234375,0.75} 1.54471x& \cellcolor[rgb]{0.9306640625,0.9990234375,0.75} 1.72799x& \cellcolor[rgb]{0.896484375,0.9990234375,0.75} 1.59112x& \cellcolor[rgb]{0.943359375,0.9990234375,0.75} 1.77928x& \cellcolor[rgb]{0.9990234375,0.9501953125,0.75} 3.55946x& \cellcolor[rgb]{0.9990234375,0.9462890625,0.75} 3.68201x& \cellcolor[rgb]{0.9990234375,0.8828125,0.75} 5.71345x& \cellcolor[rgb]{0.9990234375,0.8837890625,0.75} 5.67565x\\
\hline
\end{NiceTabular}}
\caption{\label{tab:fannkuch}Benchmark of \texttt{benches/sieven.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}
\end{table}

@@

>>>>

\begin{figure}[H]
     \centering
     \begin{minipage}[b]{0.32\textwidth}
\begin{minted}[bgcolor=LightGray]{gas}
# ...
movslq 0xc(%rsp),%rax
cmp    0x10(%rsp),%rax
jae    0x1199 <main+89>
mov    0xc(%rsp),%eax
add    $0x1,%eax
mov    %eax,0xc(%rsp)
jmp    0x1179 <main+57>
# ...
     \end{minted}
     \caption{TODO}\label{fig:clang-loop}
   \end{minipage}
   \begin{minipage}[b]{0.65\textwidth}
   \begin{minipage}[b]{0.50\textwidth}
  \begin{minted}[bgcolor=LightGray]{gas}
# ...
movq	%rsi, %rax
movl	(%rax), %eax
movq	$0, %rdx
movl	%eax, %edx
movq	%rdx, %rax
movq	$0, %rbx
movl	%eax, %ebx
movq	%rdi, %rax
movq	(%rax), %rax
movq	%rax, %rdx
     \end{minted}
   \end{minipage}
   \begin{minipage}[b]{0.50\textwidth}
  \begin{minted}[bgcolor=LightGray]{gas}
# continued...
movq	%rbx, %rax
movq	%rdx, %rcx
cmpq	%rcx, %rax
movq	$0, %rdx
setb	%dl
movq	%rdx, %rax
cmpq	$0, %rax
je	_main$20
jmp	_main$17
# ...
     \end{minted}
   \end{minipage}
     \caption{TODO}\label{fig:my-loop0}
   \end{minipage}
\end{figure}
\noindent It does make sense that my compiler nearly takes 3x as many cycles considering that nearly 3x as many instructions are being executed.   Because od the way values are stored, there is literally no benefit from Briggs coalescing since no phi nodes are involved ever.
I was surprised to see Greedy and Linear 2 to be that much slower, but on second thought it makes perfect sense since loading variables from the stack before every single arithmetic/logic operation is considerably slower. What's more surprising is the fact that Tiger is nearly 4x faster than any Greedy (see Table \ref{tab:loopn0.tig}).
It's presumably just because all binary operations consist of  about three instructions or so.

@@

Integer factorization is another interesting algorithm. Generally considered to be NP, here are the results of factorizing known primes of inreasing bit size seen in Table \ref{tab:factori32}

@@

@@

\noindent What's more interesting is that increasing the input size actually reduces the discrepancy with the Greedy and Linear 2 allocators, while all others seem to rise at the same pace as can be seen in Table \ref{tab:factori64}.

@@

\caption{\label{tab:factori64}Benchmark of \texttt{benches/factori64.ll} output by \mintinline{bash}{dune exec bench -- -f factori64 -n 1024}}

@@

 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 150790& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99873x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00204x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00055x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00202x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00475x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99925x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99983x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00036x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 266858& \cellcolor[rgb]{0.939453125,0.9990234375,0.75} 1.76227x& \cellcolor[rgb]{0.951171875,0.9990234375,0.75} 1.81025x& \cellcolor[rgb]{0.8095703125,0.9990234375,0.75} 1.24026x& \cellcolor[rgb]{0.93359375,0.9990234375,0.75} 1.73967x& \cellcolor[rgb]{0.93359375,0.9990234375,0.75} 1.73845x& \cellcolor[rgb]{0.9326171875,0.9990234375,0.75} 1.73599x& \cellcolor[rgb]{0.939453125,0.9990234375,0.75} 1.76279x& \cellcolor[rgb]{0.9990234375,0.8681640625,0.75} 6.18927x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 332932& \cellcolor[rgb]{0.8681640625,0.9990234375,0.75} 1.47463x& \cellcolor[rgb]{0.896484375,0.9990234375,0.75} 1.58958x& \cellcolor[rgb]{0.7734375,0.9990234375,0.75} 1.09780x& \cellcolor[rgb]{0.7978515625,0.9990234375,0.75} 1.19567x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39187x& \cellcolor[rgb]{0.84765625,0.9990234375,0.75} 1.39397x& \cellcolor[rgb]{0.86328125,0.9990234375,0.75} 1.45798x& \cellcolor[rgb]{0.9990234375,0.8955078125,0.75} 5.30079x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 396964& \cellcolor[rgb]{0.873046875,0.9990234375,0.75} 1.49802x& \cellcolor[rgb]{0.89453125,0.9990234375,0.75} 1.58318x& \cellcolor[rgb]{0.7578125,0.9990234375,0.75} 1.03435x& \cellcolor[rgb]{0.7607421875,0.9990234375,0.75} 1.04439x& \cellcolor[rgb]{0.8310546875,0.9990234375,0.75} 1.32655x& \cellcolor[rgb]{0.7919921875,0.9990234375,0.75} 1.16965x& \cellcolor[rgb]{0.8330078125,0.9990234375,0.75} 1.33411x& \cellcolor[rgb]{0.9990234375,0.916015625,0.75} 4.64216x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 463143& \cellcolor[rgb]{0.8193359375,0.9990234375,0.75} 1.27994x& \cellcolor[rgb]{0.8916015625,0.9990234375,0.75} 1.56894x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00193x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00219x& \cellcolor[rgb]{0.802734375,0.9990234375,0.75} 1.21525x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00036x& \cellcolor[rgb]{0.9990234375,0.9375,0.75} 3.97536x& \cellcolor[rgb]{0.9990234375,0.9208984375,0.75} 4.50366x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 528926& \cellcolor[rgb]{0.841796875,0.9990234375,0.75} 1.37202x& \cellcolor[rgb]{0.904296875,0.9990234375,0.75} 1.62053x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00265x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00090x& \cellcolor[rgb]{0.7958984375,0.9990234375,0.75} 1.18442x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00260x& \cellcolor[rgb]{0.9990234375,0.94921875,0.75} 3.59263x& \cellcolor[rgb]{0.9990234375,0.921875,0.75} 4.46336x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 594806& \cellcolor[rgb]{0.818359375,0.9990234375,0.75} 1.27651x& \cellcolor[rgb]{0.9013671875,0.9990234375,0.75} 1.60931x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.91222x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.92581x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16478x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.89116x& \cellcolor[rgb]{0.9990234375,0.955078125,0.75} 3.38589x& \cellcolor[rgb]{0.9990234375,0.921875,0.75} 4.46530x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 660398& \cellcolor[rgb]{0.84765625,0.9990234375,0.75} 1.39599x& \cellcolor[rgb]{0.9013671875,0.9990234375,0.75} 1.60987x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.89423x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90015x& \cellcolor[rgb]{0.7861328125,0.9990234375,0.75} 1.14754x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90032x& \cellcolor[rgb]{0.9990234375,0.96484375,0.75} 3.08470x& \cellcolor[rgb]{0.9990234375,0.935546875,0.75} 4.02611x\\

@@

@@

Certainly the selection of benchmarks could also have been broader, with the cast majority just showing how Greedy is considerably slower. Not to mention more benchmarks with support for the Tiger compiler that was written the year prior. Likewise, some more detailed profiling of the entire compilation would have been interesting. Some
